Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-05-11 Manuscript/manuscript.Rmd
fixed latex formatting

We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines $L = \{\textit{GM12878}, \textit{K562}\}$, at four different resolutions $R = \{\textit{10 kb}, \textit{25 kb}, \textit{50 kb}, \textit{100 kb\}}$. [??? Bad spacing, for the whole paragraph. Why you are not using plain and simple Markdown?] For each classifier, we considered 3 separate predictor types as the feature space including $P = \{\textit{OC}, \textit{OP}, \textit{Distance}\}$. To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including $B = \{\textit{None}, \textit{RUS}, \textit{ROS}, \textit{SMOTE}\}$. Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), $C = \{ 1, 2, ..., 22 \}$. A system produced from the ensemble framework was defined as: $S = \{\textit{c}, \textit{r}, \textit{p}, \textit{b}\}$, where $l \in L$, $r \in R$, $p \in P$, $b \in B$, and $c \in C$. Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2016 (= 2 \times 4 \times 3 \times 4 \times 21)$ separate models.

>>>>

We compared the performances of random forest classification models implemented on TAD boundaries called using the arrowhead algorithm [@durand2016juicebox] from replicate Hi-C data for 2 cell lines *L* = { *GM12878*, *K562* }, at four different resolutions *R* = { *10 kb*, *25 kb*, *50 kb*, *100 kb* }. For each classifier, we considered 3 separate predictor types as the feature space including *P* = {*OC*, *OP*, *Distance* }. To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling, including *B* = {*None*, *RUS*, *ROS*, *SMOTE* }. Each combination of the above parameters was repeated 21 times (number of autosomal chromosomes, excluding chromosome 9), *C* = {*1*, *2*, ..., *22*}. A system produced from the ensemble framework was defined as: *S* = {*c*, *r*, *p*, *b*}, where *l* $\in$ *L*, *r* $\in$ *R*, *p* $\in$ *P*, *b* $\in$ *B*, and *c* $\in$ *C*. Letting *|X|* denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2016 (= 2 $\times$ 4 $\times$ 3 $\times$ 4 $\times$ 21) separate models.
